---
title: "p8105_hw5_cl4044"
author: "Chenxi Liu"
date: "11/14/2020"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 8,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



```{r}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") %>% 
  nest(data = resolved)
```





## Problem 2

Iterate and import the longitudinal dataset
```{r, message=FALSE}
path_df = 
  tibble(
    path = list.files("lda_data"),
  ) %>% 
  mutate(
    path = str_c("lda_data/", path),
    data = map(.x = path, ~read_csv(.x))
  )
```

Tidy and manipulate the results
```{r}
lda_df = path_df %>%
  unnest(data) %>%
  mutate(
    name = str_extract(path, "(exp_[0-9][0-9]|con_[0-9][0-9])"),
  ) %>%
  separate(name, into = c("arm","id"), sep= "_") %>%
  pivot_longer(week_1:week_8, names_to = "week", values_to = "value", names_prefix = "week_") %>%
  select(-path) %>%
  mutate(arm_id = str_c(arm, id, sep= "_"))
```

Make a spaghetti plot showing observations on each subject over time

```{r}
lda_df %>%
  ggplot(
    aes(x = week,
        y = value,
        group = arm_id,
        color = arm_id
        )
  ) +
  geom_line() +
  facet_grid(. ~ arm) +
  labs(x = "Week", y = "Value of obervation", title = "Spaghetti plot of observations on each subject over time")

```

According to the spaghetti plot above, the observation values of participants in the control group overall stay the same over 8 weeks. The observation values of participants in the experimental group increased over 8 weeks 
